### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_address}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
    \caption{Memory Addressing}\label{fig:memory_address}
\end{figure}

In modern CPUs, L1 and L2 caches are traditional N-way set associate caches. That is, the cache is divided into several cache sets, and each set is associated with several cache lines. The cache line is the atomic unit. As shown in Figure~\ref{fig:memory_address}, when the cache is accessed, the CPU uses the \textsf{Index} field of the address to locate a cache set. After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line. If the CPU can locate a cache line with the same tag, then a cache hit occurs. The CPUs use a similar process to manage the main memory. The main memory is divided into many pages. As shown in Figure~\ref{fig:memory_address}, 
the translation process keeps the bottom bits while use the top bits to map the Physical Page Numbers to Virtual Page Numbers.
